\documentclass[11pt]{article}

\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb,amsthm}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage[hidelinks]{hyperref}

\newtheorem{theorem}{Theorem}
\newtheorem{lemma}{Lemma}
\newtheorem{proposition}{Proposition}
\newtheorem{corollary}{Corollary}
\newtheorem{heuristic}{Heuristic}
\newtheorem{remark}{Remark}

\newcommand{\F}{\mathbb F}
\newcommand{\Bnum}{B_{\rm num}}
\newcommand{\Deltaone}{\Delta_1}
\newcommand{\Deltazero}{\Delta_0}
\newcommand{\tauone}{\tau_1}
\newcommand{\tautwo}{\tau_2}
\newcommand{\tauthree}{\tau_3}
\newcommand{\Ctwo}{C_2}
\newcommand{\qline}{q_{\rm line}}
\newcommand{\qgen}{q_{\rm gen}}

\title{Experimental Theorems for Paper B's F1 / Slack-Two Resonance Window}
\author{RS-MCA experimental notes}
\date{June 18, 2026}

\begin{document}
\maketitle

\begin{abstract}
This note records restricted experimental theorems and heuristics extracted
from the Cycle 14--18 audits in the RS-MCA repository.  The main new item is a
divisibility gate for the non-coprime resonance branch in the
quadratic-extension, slack-two, three-co-support toy window.  The statements
are aimed at Paper B's residue-line normal form and per-fiber collision
program, but they are not a proof of the corrected MCA conjecture and have no
direct protocol consequence.

The note also records an attribution audit for a separate AI-generated packet
whose item (d) overlapped substantially with Theorem 1.13 of Ben-Sasson,
Carmon, Habock, Kopparty, and Saraf, \emph{On proximity gaps for
Reed--Solomon codes}, to appear at STOC 2026.  That overlap should be treated
as an imported external theorem/proof pattern, not as a new contribution of
this repository.
\end{abstract}

\section{Status and Scope}

All results in this note live in the experimental folder and should be read as
restricted algebraic facts or proof targets.  We do not edit or supersede the
main papers A--D.

The source map is:
\begin{itemize}
\item Paper A, \texttt{tex/RS\_disproof\_v3.tex}, refutes the old no-slack
  smooth-domain support-wise line-MCA statement.
\item Paper B, \texttt{tex/slackMCA\_v3.tex}, is the main target here.  In
  particular, this note is a small local contribution to the residue-line
  normal form around \texttt{def:residue}, \texttt{thm:normalform},
  \texttt{prob:perfiber}, and \texttt{conj:B}.
\item Paper D, \texttt{tex/cs25\_cap\_v4.tex}, gives the universal field-size
  cap and imported list-to-agreement route.  Nothing below changes that cap.
\item Paper C, \texttt{tex/snarks\_v4.tex}, records protocol ledgers.  Nothing
  below may be consumed by a protocol without a separate conversion theorem.
\end{itemize}

The common restricted setting is
\[
  B=\F_p,\qquad F=\F_{p^2},\qquad D=\F_p,\qquad
  t=\sigma=2,\qquad j=3,
\]
and we work off the tangent/global endpoint
\[
  R_0=\{\, [W]_E\wedge [\Bnum]_E=0\,\}.
\]
The field ledgers remain distinct:
\[
  \qgen=p,\qquad \qline=p^2.
\]
The regime is sub-reserve, since \(\eta=\sigma/n=2/n\).  Thus none of the
following proves a corrected-reserve list, CA, MCA, line-decoding, SNARK, or
protocol theorem.

\section{External Proximity-Gap Attribution Audit}

\textbf{Status: AUDIT / ATTRIBUTION.}
This section concerns a separate AI-generated packet with four advertised
results, labeled here only as (a)--(d).  It should guide later edits to the
main papers, but it is not itself a new theorem.

The cited external source is:
\[
  \href{https://www.math.toronto.edu/swastik/rs-proximity-gaps-2025.pdf}
  {\text{Ben-Sasson--Carmon--Habock--Kopparty--Saraf,
  \emph{On proximity gaps for Reed--Solomon codes}}}.
\]
Swastik Kopparty's paper page lists the same paper with coauthors Eli
Ben-Sasson, Dan Carmon, Ulrich Habock, and Shubhangi Saraf.  The paper is
reported to appear at STOC 2026.  The relevant result to audit against is
Theorem 1.13, with the subgroup/sumset construction and proof pattern around
Theorem 7.1.

\subsection*{Attribution correction}

Any repository text or AI output claiming the proof of result (d) as a new
contribution should be treated as incorrect.  The proof strategy of (d) is,
up to notation and presentation, essentially the proof of Theorem 1.13 in the
external proximity-gap paper.  In particular, even notation such as using
\(\ell\) for the size of the chosen subset appears to track the external
paper closely enough that the safe status is:
\[
  \text{result (d): imported theorem/proof pattern, not original.}
\]
Before any main-paper promotion, the text should cite the external theorem,
state exactly which hypotheses are being imported, and explain whether the
RS-MCA notation changes the object or merely renames it.

\subsection*{How to treat the four advertised results}

\begin{center}
\begin{tabular}{p{0.12\linewidth}p{0.36\linewidth}p{0.40\linewidth}}
\textbf{Item} & \textbf{Current limitation} & \textbf{Main-paper handling} \\
\hline
(a) & Works only at slack on the order of \(1/\sqrt n\). &
Use at most as a weak-slack comparison point.  It does not clear Paper B's
corrected-reserve objective and should not be stated as evidence for
capacity-minus-explicit-floors MCA. \\
(b) & Applies only to three Fermat-prime cases. &
Treat as finite-prime evidence or a worked example.  It is not a uniform
smooth-domain theorem and should not be allowed to drive asymptotic claims. \\
(c) & Requires exponential field size. &
Treat as a large-field construction or sanity check.  It is not directly
usable for the polynomial-field or Proximity Prize parameter ledger. \\
(d) & Most mathematically relevant, but the proof is essentially external. &
Import, cite, and adapt from Theorem 1.13 of the proximity-gap paper.  Do not
present it as an AI/repository proof.  Audit the exact object before using it
in Paper B, D, or C. \\
\end{tabular}
\end{center}

\subsection*{Main-paper integration plan}

\textbf{Paper B.}
Add a related-work and dependency paragraph near the local-limit/frontier
discussion saying that the proximity-gap theorem of Ben-Sasson--Carmon--
Habock--Kopparty--Saraf is the source for the item-(d) proof pattern.  If a
Paper B statement uses the theorem, state it as an imported theorem with exact
parameters: domain, rate, slack, field-size regime, and whether the object is
a proximity gap, list statement, CA/MCA statement, or line-decoding statement.
Do not let the \(1/\sqrt n\)-slack result (a), the three-Fermat-prime result
(b), or the exponential-field result (c) substitute for the corrected-reserve
MCA conjecture.

\textbf{Paper D.}
Keep the Crites--Stewart list-to-agreement import separate from this
proximity-gap import.  If item (d) is relevant to the universal-cap narrative,
it should be cited as external background or as a separately imported theorem,
not folded into the cap proof unless the field ledger and radius normalization
are checked line by line.

\textbf{Paper C.}
Protocol ledgers should not consume item (d) merely because it is a
Reed--Solomon proximity theorem.  A protocol-facing use still needs a precise
conversion into the consumed object: base-list size, interleaved-list size,
CA, MCA, line-decoding, or curve-MCA.  Until such a conversion is proved, the
ledger status is \textsc{conditional/imported} at best.

\textbf{Paper A.}
No change is forced.  These results do not rescue the old no-slack smooth
support-wise MCA theorem refuted by Paper A.  They should be cited only if
they clarify the landscape around proximity gaps and explicit slack regimes.

\subsection*{Notation hygiene}

When this material is eventually moved into the main papers, avoid copying the
external notation silently.  If the external proof uses \(\ell\) for a chosen
subset size, either keep that notation with an explicit citation or rename it,
for example to \(\ell_{\rm pg}\), so it is not confused with RS-MCA slack
\(t,\sigma\), support size, list size, or line-decoding parameters.  The
ledger notation must still distinguish \(q_{\rm gen}\), \(q_{\rm line}\),
\(q_{\rm chal}\), \(B\), and \(F\).

\subsection*{Checklist before promotion}

\begin{itemize}
\item Add a BibTeX entry for the proximity-gap paper before citing it in
  Papers A--D.
\item Replace any claim of ``new proof of (d)'' by ``adapted from
  Theorem 1.13 of Ben-Sasson--Carmon--Habock--Kopparty--Saraf.''
\item Verify whether item (d)'s theorem object is list/proximity, CA, MCA,
  line-decoding, or something only convertible under an additional theorem.
\item Record which of (a)--(d) operate at \(1/\sqrt n\) slack, three Fermat
  primes, exponential field size, and imported-theorem status.
\item Re-run the field ledger: do not let an extension field pay a
  generated-field entropy bill unless the cited theorem explicitly does so.
\end{itemize}

\section{Notation}

The base/generated field is \(B=\F_p\).  The line field is the quadratic
extension \(F=\F_{p^2}=B(\alpha)\), with basis \(\{1,\alpha\}\) over \(B\) and
\(\alpha^2=\nu\in B\).  The domain is \(D=\F_p\), so \(n=|D|=p\).

A degree-two residue-line datum consists of:
\[
  E\in F[X],\qquad \deg E=2,\qquad E(x)\ne0\ \text{for all }x\in D,
\]
and a numerator
\[
  \Bnum\in F[X],\qquad \deg \Bnum<2.
\]
We write
\[
  A=F[X]/E,\qquad [P]_E\in A,\qquad b=[\Bnum]_E.
\]
The anchor word on \(D\) is interpolated by a polynomial \(W\).  The operation
\(u\wedge v\) means the determinant of the coordinate vectors of
\(u,v\in A\) in a chosen \(F\)-basis of the two-dimensional \(F\)-space \(A\).
Off \(R_0\), the pair \(\{[W]_E,b\}\) is such a basis.

The co-support has size \(j=3\).  If \(T\subset D\) is the three-point
co-support, define
\[
  \tau_1=e_1(T),\qquad \tau_2=e_2(T),\qquad \tau_3=e_3(T).
\]
All valid co-supports have \(\tau_i\in B\).  The quantity \(\Ctwo\) denotes
the number of distinct slopes produced by the relevant landing branch after
restricting to valid split triples \(T\subset\F_p\).  Bounding landing points
therefore bounds \(\Ctwo\), but a sharp slope theorem may require more because
many landing points can share a slope.

\section{Cycle 14 Normal Form}

The Cycle 14 audit reduces the \(t=2,j=3\) landing equation to two affine
forms in the elementary co-support parameters
\[
  \tau=(\tauone,\tautwo,\tauthree).
\]

\begin{lemma}[Affine wedge normal form]
\label{lem:affine-wedge}
Assume \(\{[W]_E,b\}\) is an \(F\)-basis of \(A\).  Then the landing equation
can be written in the form
\[
  \iota(\tau)=A_0(\tauone,\tautwo)-\tauthree [W]_E,\qquad
  \mu(\tau)=B_0(\tauone,\tautwo)-\tauthree b,
\]
where
\[
  A_0=p_1[W]_E+p_2 b,\qquad B_0=q_1[W]_E+q_2 b,
\]
and \(p_i,q_i\in F\) are affine-linear functions of
\((\tauone,\tautwo)\).  If the basis is normalized so
\([W]_E\wedge b=1\), then
\[
  \Delta=\iota\wedge\mu
    =(p_1-\tauthree)(q_2-\tauthree)-p_2q_1.
\]
\end{lemma}

\begin{proof}
The Cycle 14 quotient calculation, which is a concrete instance of Paper B's
residue-line normal form, gives the displayed affine forms.  Expanding in the
ordered basis \(\{[W]_E,b\}\), the coordinate vector of \(\iota\) is
\((p_1-\tauthree,p_2)\), while the coordinate vector of \(\mu\) is
\((q_1,q_2-\tauthree)\).  Their wedge determinant is therefore
\[
  (p_1-\tauthree)(q_2-\tauthree)-p_2q_1.
\]
\end{proof}

\section{Cycle 18 Component Split}

Choose a basis \(F=B+\alpha B\) with \(\alpha^2=\nu\in B\), and write
\[
  p_1=p_{10}+\alpha p_{11},\quad
  p_2=p_{20}+\alpha p_{21},\quad
  q_1=q_{10}+\alpha q_{11},\quad
  q_2=q_{20}+\alpha q_{21}.
\]
Split
\[
  \Delta=\Deltazero+\alpha\Deltaone,\qquad
  \Deltazero,\Deltaone\in B[\tauone,\tautwo,\tauthree].
\]

\begin{theorem}[Monic quadratic and linear alpha component]
\label{thm:component-split}
In the setting above,
\[
\begin{aligned}
\Deltazero={}&
  \tauthree^2-(p_{10}+q_{20})\tauthree
  +p_{10}q_{20}+\nu p_{11}q_{21}
  -p_{20}q_{10}-\nu p_{21}q_{11},\\
\Deltaone={}&
  -(p_{11}+q_{21})\tauthree
  +p_{10}q_{21}+p_{11}q_{20}-p_{20}q_{11}-p_{21}q_{10}.
\end{aligned}
\]
Consequently \(\Deltazero\) is monic quadratic in \(\tauthree\), while
\(\Deltaone\) has degree at most one in \(\tauthree\).
\end{theorem}

\begin{proof}
Substitute the coordinate expressions for \(p_i,q_i\) into the identity of
Lemma~\ref{lem:affine-wedge} and use \(\alpha^2=\nu\).  Collecting the
coefficient of \(1\) gives the displayed formula for \(\Deltazero\), and
collecting the coefficient of \(\alpha\) gives the displayed formula for
\(\Deltaone\).  The coefficient of \(\tauthree^2\) in \(\Deltazero\) is \(1\),
and the \(\alpha\)-component has no \(\tauthree^2\)-term.
\end{proof}

\begin{corollary}[Graph reduction outside the zero-alpha branch]
\label{cor:graph}
If \(\Deltaone\) is not the zero polynomial, write
\[
  \Deltaone=s(\tauone,\tautwo)\tauthree+h(\tauone,\tautwo).
\]
On the open locus \(s\ne0\), the common-zero condition
\(\Deltazero=\Deltaone=0\) is supported on the graph
\[
  \tauthree=-h/s.
\]
\end{corollary}

\begin{proof}
This is immediate from solving the linear equation \(\Deltaone=0\) for
\(\tauthree\) on \(s\ne0\).
\end{proof}

\section{New Divisibility-Gate Theorem}

The next theorem is the main new theorem extracted from the Cycle 18
reduction.  It is stronger than merely saying that the branch is a graph: it
shows that any two-dimensional family must satisfy an explicit divisibility
identity.

\begin{theorem}[Divisibility gate for the graph branch]
\label{thm:divisibility-gate}
Assume the restricted setting above and assume \(\Deltaone\ne0\).  Write
\[
  \Deltaone=s(\tauone,\tautwo)\tauthree+h(\tauone,\tautwo),
\]
and define the denominator-cleared graph polynomial
\[
  G(\tauone,\tautwo)
  =s(\tauone,\tautwo)^2
    \Deltazero\bigl(\tauone,\tautwo,-h(\tauone,\tautwo)/s(\tauone,\tautwo)\bigr).
\]
Then \(\deg G\le 4\).  If \(G\) is not the zero polynomial, then
\[
  \#\{\,\tau\in B^3:\Deltazero(\tau)=\Deltaone(\tau)=0\,\}=O(p).
\]
Consequently the corresponding number of distinct slopes satisfies
\[
  \Ctwo=O(p)=O(n).
\]
Therefore a growing-prime family with
\[
  \Ctwo=\Theta(p^2)=\Theta(\qline)
\]
in the nonzero-\(\Deltaone\) branch can occur only if \(G\equiv0\).
\end{theorem}

\begin{proof}
Because the \(p_i,q_i\) are affine-linear in \((\tauone,\tautwo)\), the
coefficient \(s\) has degree at most \(1\), and \(h\) has degree at most \(2\).
Since \(\Deltazero\) is monic quadratic in \(\tauthree\), clearing the
denominators after substituting \(\tauthree=-h/s\) gives a polynomial \(G\) of
degree at most \(4\).

On \(s\ne0\), the equation \(\Deltaone=0\) forces
\(\tauthree=-h/s\).  Hence every common zero on this open locus gives a base
pair \((\tauone,\tautwo)\) with \(G(\tauone,\tautwo)=0\).  If \(G\) is nonzero,
Schwartz--Zippel gives at most \(4p\) such base pairs, and each base pair gives
at most one value of \(\tauthree\).

It remains to count the exceptional locus \(s=0\).  There
\(\Deltaone=0\) also forces \(h=0\).  If \(s\) is a nonzero affine form, this
is contained in an affine line; if \(s\equiv0\), then \(h\) is a nonzero
polynomial of degree at most \(2\).  In either case there are \(O(p)\) base
pairs.  For each such pair, \(\Deltazero\) is a monic quadratic in
\(\tauthree\), so it gives at most two values of \(\tauthree\).  The total
common-zero count is \(O(p)\).

Finally, the number of distinct slopes is bounded by the number of landing
points \(\tau\).  Thus \(\Ctwo=O(p)\) whenever \(G\not\equiv0\), and any
\(\Theta(p^2)\) family in this branch must satisfy \(G\equiv0\).
\end{proof}

\begin{remark}
The identity \(G\equiv0\) says that, after clearing the \(s\)-denominator,
\(\Deltazero\) is divisible by the linear equation \(\Deltaone\) on the graph
branch.  This is now the first exact algebraic gate that a large slope family
must pass.
\end{remark}

\section{Nearby Proven Gates}

The same restricted lane contains two other useful gates.  They are included
here because they explain where the new theorem fits.

\begin{proposition}[Base-component complete-intersection gate]
\label{prop:complete-intersection}
Suppose \(\Deltazero,\Deltaone\in B[\tauone,\tautwo,\tauthree]\) have no common
surface component.  Then
\[
  \#V(\Deltazero,\Deltaone)(B)=O(p),
\]
and hence this branch contributes \(\Ctwo=O(p)\) slopes.
\end{proposition}

\begin{proof}
The two components have bounded degree.  If they share no surface component,
their common zero set in \(\mathbb A^3_B\) is a curve of bounded degree.  A
bounded-degree affine curve over \(\F_p\) has \(O(p)\) rational points, and
slopes are bounded by landing points.
\end{proof}

\begin{proposition}[Cycle 16 determinant gate]
\label{prop:det-gate}
Let \(Q(z_0,z_1)\) be the Cycle 15--16 determinant consistency polynomial for
the affine system
\[
  L_z(\tau)=\iota(\tau)-z\mu(\tau)=0,\qquad z=z_0+\alpha z_1.
\]
If \(Q\) is not identically zero, then in the restricted \(D=\F_p\),
\(t=\sigma=2\), \(j=3\), off-\(R_0\) window,
\[
  \Ctwo\le 4p=O(p)=O(n).
\]
\end{proposition}

\begin{proof}
Cycle 16 gives \(\deg Q\le4\) and shows that every landing slope must satisfy
\(Q(z_0,z_1)=0\).  If \(Q\ne0\), Schwartz--Zippel over \(B=\F_p\) gives at
most \(4p\) possible pairs \((z_0,z_1)\), hence at most \(4p\) slopes.
\end{proof}

\section{Slope Map and Remaining Heuristics}

On the graph branch, the landing equation \(\iota=z\mu\) gives
\[
  p_1-\tauthree=zq_1,\qquad p_2=z(q_2-\tauthree).
\]
Where \(q_1\ne0\), substituting \(\tauthree=-h/s\) yields
\[
  z(\tauone,\tautwo)=\frac{p_1+h/s}{q_1}.
\]
Equivalently, eliminating \(\tauthree\) recovers the Cycle 14 quadratic
\[
  q_1z^2-(p_1-q_2)z-p_2=0,
\]
so the residual map is controlled by
\[
  (\tauone,\tautwo)\longmapsto [\,q_1:(p_1-q_2):p_2\,]\in\mathbb P^2(F).
\]

\begin{heuristic}[Exceptional identity should be rare]
For generic source data, the polynomial \(G\) should not vanish identically.
Thus the graph branch should usually be curve-sized, and the first possible
large-slope families should come from algebraically special data satisfying
the divisibility identity \(G\equiv0\) or from the zero-alpha branch
\(\Deltaone\equiv0\).
\end{heuristic}

\begin{heuristic}[What remains after the gate]
If \(G\equiv0\), the problem is no longer to show that the common-zero set is
small.  It may be surface-sized.  The remaining question is whether the
projective coefficient map has one-dimensional image on every source-valid
surface, giving \(\Ctwo=O(p)\), or whether some growing-prime source-valid
family has two-dimensional image and \(\Ctwo=\Theta(p^2)\).
\end{heuristic}

\section{Next Experimental Checks}

A useful scanner should compute, for each source-valid candidate:
\[
  \Deltaone=s\tauthree+h,\qquad
  G=s^2\Deltazero(\tauone,\tautwo,-h/s),
\]
then record whether \(G\equiv0\), whether \(\Deltaone\equiv0\), the
exceptional locus \(s=h=0\), the image size of
\[
  [\,q_1:(p_1-q_2):p_2\,],
\]
and the direct slope count over distinct split triples \(T\subset\F_p\).

The certificate should keep at least:
\[
\begin{gathered}
  p,\ \qgen,\ \qline,\ E,\ \Bnum,\ \text{seed},\ \text{stratum},\
  R_0\text{-status},\\
  \Deltaone\equiv0,\quad G\equiv0,\quad
  \#\{s=h=0\},\quad \#\operatorname{image},\quad
  \Ctwo,\quad \#\{T\text{ split distinct}\}.
\end{gathered}
\]

\section{Non-Claims}

This note does not claim:
\begin{itemize}
\item a proof of the corrected MCA conjecture;
\item a positive theorem above corrected reserve;
\item a \(\qgen\) local-limit theorem;
\item a list, CA, MCA, line-decoding, SNARK, or protocol consequence;
\item a large \(\Theta(p^2)\) counterpacket.
\end{itemize}

The mathematical value is narrower: the possible large branch in this
restricted window must satisfy an explicit algebraic identity before it can
even be surface-sized.

\end{document}
